|

### 2023-05-11 manuscript/paper.Rmd
If you just use align without the $$ you get numbering.

$$
\begin{aligned}
X_{ti} \iid \left\{\begin{array}{ll} \mathcal{N}(\theta_f + u_{ft},\sigma^2), & W_{ti} = \text{Female} \\ \mathcal{N}(\theta_m + u_{mt},\sigma^2), & W_{ti} = \text{Male} \end{array}\right.
\end{aligned}
$$
In this setting, for $g \in \{f,m\}$, $\theta_g$, is the defined as the overall mean of the phenotype of interest for each gender, and $u_{gt}$ are the gender specific random effects, measuring the difference between the gender and time-specific mean and the overall gender-specific mean, which we fit to an autoregressive process of lag 1, which is the discretization of an OU process.  For $t = 2,\ldots,T$ and $g \in \{f,m\}$, the AR1 model for is defined as

>>>>

\begin{align}
X_{ti} \iid \left\{\begin{array}{ll} \mathcal{N}(\theta_f + u_{ft},\sigma^2), & W_{ti} = \text{Female} \\ \mathcal{N}(\theta_m + u_{mt},\sigma^2), & W_{ti} = \text{Male} \end{array}\right. 
\end{align}

In this setting, for $g \in \{f,m\}$, $\theta_g$, is the defined as the overall mean of the phenotype of interest for each gender, and $u_{gt}$ are the gender specific random effects, measuring the difference between the gender and time-specific mean and the overall gender-specific mean, which we fit to an autoregressive process of lag 1, which is the discretization of an OU process.  For $t = 2,\ldots,T$ and $g \in \{f,m\}$, the AR1 model for is defined as
